Improving Usability of Remote Access to Sensitive Data

### 2014-07-25 ccsw14/paper.tex
release auditing

Since users ultimately require some method for releasing the results of their
research, qemu was configured to create a channel through the serial port on the
VM to a UNIX domain socket on the host machine.  A simple daemon was written
which runs on the secure machine to listen on this socket for any results to be
released.  It follows an extremely simple protocol that takes the file name,
file size, and file data and exports them to a database where they can then
undergo a review process.  We discuss potential approaches for automating this
review process for candidate release data in Section \ref{sec:Results Audit}

@@

@@

%automating part/all of result release audit

>>>>

Since users ultimately require some method for releasing the results of their
research, qemu was configured to create a channel through the serial port on the
VM to a UNIX domain socket on the host machine.  A simple daemon was written
which runs on the secure machine to listen on this socket for any results to be
released.  It follows an extremely simple protocol that takes the file name,
file size, and file data and exports them to a database where they can then
undergo a review process.  We discuss a potential approach for automating this
review process for candidate release data in Section \ref{sec:Results Audit}

@@

Although Data Capsules aims to ease secure access to sensitive data by removing
the need to audit data and software being imported into a secure environment, it
does not address how to ease the auditing of results data being released from
that same environment.  This is a challenging issue, since a careful attacker
could use any number of methods to disguise the leaking of large amounts of data
as something that appears entirely innocent.

While there is no evident solution, there are likely many measures that could be
taken to automate the identification of more obvious leak attempts.  For
example, simply measuring the information content of a candidate for release,
say by measuring its Shannon entropy or its compressed file size, if the
candidate is unusually large then it may be immediately flagged as suspicious.
This is only the tip of the iceberg, and there are likely more elegant and
powerful solutions available.  We leave investigation into such a system as
future work.

@@
